Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
Add arch section
more on architecture

>>>>

\subsection{Architecture}\label{sec:arch}

The architecture is depicted in Figure~\ref{fig:arch}. A SPARQL
protocol implementation will accept a client's query (and could cache
it's result in its entirety, but this is neither implemented nor
depicted). Two things happen to a valid query:

\begin{itemize}
\item The query (or indeed the algebra) is sent asynchronously to a
  set of analysers that is tasked with predicting what parts of the
  incoming query may be useful to answer future queries. The result of
  the analysis is sent to a prefetcher that will decide how to fetch
  the needed data, currently it only operates on triple patterns, and
  therefore, and since it is also assumed that a triple pattern
  fragments server can answer any triple pattern, it instructs a TPF
  client to fetch and enter the result into the cache.  
\item The SPARQL protocol implementation will also send the query to
  a parser that will create an algebra tree from it. The algebra tree
  is then passed to a query engine for immediate execution. The query
  engine has an elaborate query planner that can create plans for
  accessing a cache, a TPF server and a SPARQL Endpoint. When the
  planner finishes planning, the evaluator may use a TPF client or a
  SPARQL protocol client to fetch data that is not in the cache. The
  results of single triple patterns may be inserted in the cache by
  the TPF client.
\end{itemize}

\begin{figure}[bh]
\begin{center}
\includegraphics{architecture.pdf}
\caption{Architectural overview. The proposed system is represented
  inside the box titled ``Proxy''. It interacts with a client, a
  Triple Patterns Fragments Server and a SPARQL Endpoint. The most
  important component is the query engine, which consists of a query
  planner and a query evaluator.}\label{fig:arch}
\end{center}
\end{figure}
